Joint analysis of read count data

### 2020-09-09 combined_analysis/combine_all_data.Rmd
add zenith

```{r show.gene_set_test.marginal}
res_zenith_marginal.GO[['Scz']][1:20,] %>% kable(caption="Scz") %>% kable_styling(full_width=FALSE)
res_zenith_marginal.GO[['BP']][1:20,] %>% kable(caption="BP") %>% kable_styling(full_width=FALSE)
res_zenith_marginal.GO[['Sex']][1:20,] %>% kable(caption="Sex") %>% kable_styling(full_width=FALSE)
```

>>>>

```{r show.gene_set_test.marginal}

show_zenith_results = function( resList, key, FDR = 0.05){
	df = resList[[key]]

	# filter by FDR
	df = df[df$FDR <= FDR,]

	df %>% kable(caption=key) %>% kable_styling(full_width=FALSE)
}

show_zenith_results( res_zenith_marginal.GO, "Scz")
show_zenith_results( res_zenith_marginal.MSigDB, "Scz")

show_zenith_results( res_zenith_marginal.GO, "BP")
show_zenith_results( res_zenith_marginal.MSigDB, "BP")

show_zenith_results( res_zenith_marginal.GO, "Sex")
show_zenith_results( res_zenith_marginal.MSigDB, "Sex")
```
